The BitShares network offers financial instruments for everyone to use at a low
fee.
%
% DEX
The decentralized exchange (DEX) allows for trade of any arbitrary pair of
assets issued on the BitShares blockchain. The order-matching algorithm is
equivalent to most central exchanges and allows to directly fill an existing
given order or walk-the-books up to a given price by means of a limit order.
%
% MPA
With SmartCoins, the BitShares ecosystem offers a powerful tool for everyone
from speculators and savers, to traders and entrepreneurs. The BitShares
platform provides a toolset with which innovators can experiment to find
optimal currency solutions using free market discovery. It was shown that in
order to achieve a price \emph{predictability}, a price floor of \$1.00 USD per
bitUSD is most reasonable. Hence, any long position can be settled at the
current price of the underlying asset.
%
% UIA
Additionally, we have shown that user issued assets (UIA) offer countless
opportunities to reduce costs. Not only can they be used to simply store a
token on a decentralized database (the blockchain), but it was also shown that
IOUs can be issued complying with regulations. Since the BitShares network
takes care of order processing in storage of user balances, an implementation
of UIAs come at almost no cost while obsoleting expensive central server
infrastructure. 
%
% %% Bonds
% The Bitshares bond market allows investors who wish to gain leverage in a
% particular asset to offer competitive interest rates to those willing to
% commit capital for a specified time. The implementation of a bond market on a
% blockchain consensus system efficiently reduces the overhead and counterparty
% risk typically associated with such contracts.
%

In this paper, we have laid out the foundations of the BitShares network aimed
to shift the paradigm of classical banking towards a large scale peer-to-peer
financing.
