Crypto-currencies depend upon a public ledger or blockchain, which makes
privacy challenging, because everyone can see every transaction. Bitcoin gives
every user one or more account numbers, and that gives many people a false
sense of security. People assume that as long as no one knows their account
number and they use a new account number with every transaction, it is
impossible to tie their bitcoins to their real life identify.

This is where the large centralized exchanges become a problem. In order to
comply with government regulations, exchanges must know everyone they do
business with. Since many bitcoin transactions flow through an exchange, the
exchange learns who everyone is and can start to track who is doing business
with whom. Coinbase is already closing accounts~\cite{coinbase:privacy} based
upon who you do business with after withdrawing your bitcoins.

In order to have even the slightest bit of privacy, the exchange functionality
needs to be divided among hundreds of parties who are unlikely to collude to
compromise identity. This is not economically practical today, because the
exchange order book creates market incentives that naturally tend toward
centralization in just a few exchanges with the vast majority of market share.

In BitShares, your identity need only be verified by issuers of IOUs (e.g.
GateUSD) in order to comply with fiat regulations. Once traded for bitUSD your
link to the gateway or exchange \emph{Gate} can be removed quickly by means of
\emph{blinded transactions} that enables users to publicly move funds without
revealing the exact amount~\cite{bts:general,blindSigPaper}. If issuers
approve, blinded transactions may even be performed for UIAs directly.
