\label{sec:mpa}

A crypto-currency, with the properties and advantages of Bitcoin, that is
capable of maintaining price parity with a globally adopted currency (e.g.
U.S. dollar), has high utility for convenient and censorship resistant
commerce. This can be achieved by BitShares' market pegged assets (MPA), a new
type of freely traded digital asset whose value is meant to track the value of
a conventional underlying asset by means of contracts for difference (CFD). 

A \emph{SmartCoin} (synonym for MPA) is a crypto-currency that \emph{always}
has 100\% or more of its value backed by the BitShares core currency (BTS), to
which they can be converted at any time, as \emph{collateral} in a CFD.

What makes MPAs unique is that they are free from counterparty risk even though
they resemble a CFD backed by collateral. This is achievable by letting the
network itself (implemented as a software protocol) be responsible for securing
the collateral and performing settlements as will be described in more detail
below.

% at an exchange rate set by a trustworthy price feed\footnote{Price feeds are
% published by witnesses that have shareholder approval.}. 

% While certain risks of the system have been outlined, no system is
% without risk. The current banking system allows private funds to be frozen or
% confiscated without consent, such as by court order or administrative actions.
% Traditional banks and financial institutions are susceptible to insolvency.
% The availability and quality of banking service varies greatly throughout the
% world. 

We will present SmartCoins as a viable open source alternative to the expensive
banking system. Achieving price parity with a commonly used currency
facilitates pricing and acceptance by merchants. Additionally it reduces the
need to calculate capital gains and losses on volatile assets to determine tax
liability. In short, BitShares brings \emph{publicly} auditable open source
banking to anyone with access to the internet. MPAs allow savers and spenders
to choose preferred asset types. This brings flexibility and ease of use to the
open source banking experience.
 
The subsequent paragraphs will explain how market pegged assets including (for
instance) \emph{BitUSD} (intended to track the value of the U.S. dollar)
achieve price parity while minimizing risk to holders.
