There is always concern of price manipulation. Someone with a large amount of
money on both sides of a trade can use their funds to manipulate the markets
and thus the price feed. If the amount of money they lose manipulating the
markets is less than the amount of money they can gain by manipulating the
price feed, then it will be profitable to manipulate the market at the expense
of either the BitUSD longs or the shorts. A low-collateralized short that sees
a large force or global settlement order requested can attempt to manipulate
the markets and thus the feed against the BitUSD holder.

The risk of price manipulation should be priced into the premium on BitUSD
charged by the shorts, and thus should already be priced into the market. If
price manipulation became a serious problem that caused very high premiums,
then it could be addressed by the price feed producers, who can adopt a moving
average over wider time windows to increase the difficulty of short-term
manipulation. A variety of algorithms could be used to estimate a \emph{fair
price}\footnote{``fair'' for honest market participants.} that keeps BitUSD
valued at least \$1.00.

In practice, a feed producer can observe the BitUSD:USD market as an indicator
on which way to adjust the feed. Generally speaking, the strategy that the feed
producers adopt for controlling the feed should be public knowledge, because
the shorts will ultimately rely on it. For the feed producers to change
strategies in unpredictable ways could cause losses to both longs and shorts.
Fortunately, it is assumed that shareholders primarily approve complying and
quickly fire misbehaving feed providers.
