Before we discuss how BitShares achieves price \emph{stability} we first need to
define what properties make a currency \emph{stable}.

In the U.S., for instance, the Federal Reserve (FED) has as a mandate of
\emph{stable prices} and it is almost universally accepted that this is a good
mandate. The same holds true for the Euro with its stability being
\emph{controlled} by the European central bank. Mostly every country/nation or
federation applies similar concepts.

It is also widely accepted among many crypto-currency fans that, in the case of
the US dollar, the FED has failed at their mandate because of persistent rise
in prices resulting in the dollar losing 99\% of its \emph{purchasing power}
since the FED was founded in 1913. As a result people in the crypto currency
space are attempting to provide an alternative currency that can achieve the
FEDs mandate. The goal of price stability at its heart is the same as
\emph{price fixing} and this is a well known economic fallacy that
crypto-currencies should avoid.

The goal of the FED price stability mandate is to mask the systematic theft of
all increases in the production efficiency of the economy. Lets assume the FED
managed to keep prices stable through their monetary policy with 0\% price
inflation over 20 years. Now lets assume that during this same 20 years the
invention of the computer and Internet resulted in a 3x increase in efficiency
and thus there are now 3x as much food, cars, phones, houses, etc. For the sake
of this example we will assume the population is the same and everyone has the
same amount of money in the bank. You would normally expect that everything
would be 1/3 the price and that everyone would be able to afford 3x their prior
life style. But because of FED intervention they have managed to also increase
the money supply by 3x and distribute it to their friends. The end result is
that some people get a 1000x increase in life style while everyone else stands
still.

We can conclude from this that the mandate for price stability is a goal meant
to mislead the general public and mask theft from the lower and middle classes
on a massive scale even at 0\% price inflation. It would be ridiculous to bring
this same mandate to crypto currencies which aim to free us from monetary
enslavement.

We also notice that the goals should not be \emph{price stability} nor should
we target a \emph{stable value} or \emph{purchasing power} (at least not yet). 
%
What we really want instead is 
\begin{itemize}
 \item a \emph{predictable} price with reduced volatility
 \item a unit of account that doesn't have any meaningful capital gains or
    losses for tax purposes
 \item a somewhat reliable ability to predict the future value of a token.
\end{itemize}

Hence, price ``stability'' really means price \emph{predictability} within some
tolerance level. In the case of the U.S. dollar, a willingness to accept a 5\%
loss (in purchasing power) per year demonstrates that predictability is more
important than stability~\cite{bm:stable:impossible}.
