\label{sec:uia:priv}

Price-stable crypto-currencies (a.k.a. SmartCoins) were the inspiration for
BitShares. Now, users can create their own price-stable assets with custom
parameters designed to track the value of any asset they can imagine. The
benefit of price-stable crypto-currencies is that they are fully
collateralized, and the issuer only needs to be trusted to appoint an honest
set of independent (non-collusive) feed producers. Unlike deposit receipts, the
value of a privatized SmartCoin is secured even if the issuer disappears (in
this case, however, the asset may be declared non-complying by regulators since
white- and black-lists cannot be updated any longer).

Bitshares provides many parameters that an issuer may tune. In addition to
account whitelists, market restrictions, and transfer restrictions, the issuer
of a private SmartCoin has control over:

\begin{enumerate}
 \item Collateral Type
 \item Initial Collateral Rate
 \item Maintenance Collateral Rate
 \item Forced Settlement Fee, Delay %, and Daily Volume %% (???????)
 \item Price Feed Update Rate
 \item Global Forced Settlement
 \item Trading and Withdrawal Fees
\end{enumerate}

With these tools it is possible to emulate a pure contract for difference with
periodic global forced settlement (i.e., monthly, yearly, etc), or to emulate
BitShares 1.0 BitAssets by having a 30 day delay on forced settlement.

Arbitrary financial indexes can be used for the price feed to mimic all manner
of exotic assets. In addition with publicly auditable accounts even mixed asset
funds can be modelled with the advantage of verifiable ownership claims by the
fund manager.
