The Graphene Platform has been developed by Cryptonomex specifically for
BitShares, went through many changes and has done its best to stay on top of
blockchain technology. One of it's public forks, BitShares, is publicly traded
for over 2 years and has yet to show it's full potential. For this reasons, we
have deployed a testnet using the very same technology that BitShares is built
on, specifically for testing algorithms, implementations and also scalability.

Here, the term \emph{scalability} refers to the amount of transactions that can
be applied to the blockchain at scale. Several factors need to be taken into
account to correctly interpret any results obtained through testing. Among
these are the specification of the deployed servers (CPU/RAM) that produce the
blocks (validators), the interconnectivity of the nodes in the Peer-2-Peer
network, the round-trip times and latency between nodes, as well as the
geographical distance between nodes.

Obviously, a globally distributed network represents the worst case scenario
when it comes to latency between nodes limited mostly by the speed of light and
the size of the planet. A network that is hosted locally can result in better
overall performance but doesn't offer the same robustness and redundancy as a
global network.

The number of validators, furthermore, does not affect the throughput as long
as all active validators can keep up with the requirements of the network. All
active validators are treated equally and are given a slot to produce their
blocks in each round~\cite{bts:general}. Increasing the number of validators
(a.k.a. witnesses) comes with an increased robustness against server failures,
but also results in a longer period to reach transaction
finality~\cite{bts:general} which describes the absolute irreversibility of
transactions after 2/3 of all validators approved a given block and its'
transactions.

The goal of the public stress-test performed on the graphene-based testnet was
to identify the limiting factors and bottlenecks at scale with multiple parties
involved. We furthermore wanted to demonstrate scalability of current state of
the art blockchain technologies.
